### 2025-06-10 simulation.qmd
20250609 - fix

```{r}
all_proj <- bind_rows(players_projectedPoints_seasonal)
```

@@

```{r}
bootstrapSimulation <- function(projectedStats, vars_by_pos, n_iter = 10000, seed = NULL) {
  dt <- data.table::as.data.table(all_proj)
  all_ids <- unique(dt$id)

@@

  future::plan(multisession)

@@

      stat_vars <- vars_by_pos[[player_pos]]
      out <- data.table::data.table(iteration = 1:n_iter, id = player_id, pos = player_pos)

>>>>

```{r}
all_proj <- dplyr::bind_rows(players_projectedPoints_seasonal)
```

@@

```{r}
bootstrapSimulation <- function(projectedStats, vars_by_pos, n_iter = 10000, seed = NULL) {
  dt <- data.table::as.data.table(projectedStats)
  all_ids <- unique(dt$id)

@@

  future::plan(future::multisession)

@@

      stat_vars <- vars_by_pos[[player_pos]]
      out <- data.table(iteration = seq_len(n_iter), id = player_id, pos = player_pos)
